\documentclass[letterpaper,10pt]{article}

% Dependencies
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{bookmark}
\usepackage{lastpage}

% Serif Fonts
\usepackage{CormorantGaramond}
\usepackage{charter}

% Colors
\usepackage{xcolor}
\definecolor{accentTitle}{HTML}{0e6e55}
\definecolor{accentText}{HTML}{0e6e55}
\definecolor{accentLine}{HTML}{a16f0b}

% Misc. Options
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\urlstyle{same}

% Adjust Margins
\addtolength{\oddsidemargin}{-0.7in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\setlength{\tabcolsep}{0pt}
\setlength{\footskip}{3.7pt}
\raggedbottom
\raggedright

% ATS Readability
\input{glyphtounicode}
\pdfgentounicode=1

% Custom Commands
\newcommand{\documentTitle}[2]{
  \begin{center}
    {\Huge\color{accentTitle} #1}
    \vspace{10pt}
    {\color{accentLine} \hrule}
    \vspace{2pt}
    \footnotesize{#2}
    \vspace{2pt}
    {\color{accentLine} \hrule}
  \end{center}
}

\newcommand{\documentFooter}[1]{
  \setlength{\footskip}{10.25pt}
  \fancyfoot[C]{\footnotesize #1}
}

\newcommand{\numberedPages}{
  \documentFooter{\thepage/\pageref{LastPage}}
}

\titleformat{\section}{
  \vspace{-5pt}
  \color{accentText}
  \raggedright\large\bfseries
}{}{0em}{}[\color{accentLine}\titlerule]

\newcommand{\tinysection}[1]{
  \phantomsection
  \addcontentsline{toc}{section}{#1}
  {\large{\bfseries\color{accentText}#1} {\color{accentLine} |}}
}

\newcommand{\heading}[2]{
  \hspace{10pt}#1\hfill#2\\
}

\newcommand{\headingBf}[2]{
  \heading{\textbf{#1}}{\textbf{#2}}
}

\newcommand{\headingIt}[2]{
  \heading{\textit{#1}}{\textit{#2}}
}

\newenvironment{resume_list}{
  \vspace{-7pt}
  \begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=30pt]
}{
  \end{itemize}
}

\renewcommand\labelitemi{--}

\begin{document}

%---------%
% Heading %
%---------%
\documentTitle{Vaishnav Dhanwate}{
  \href{tel:+918421451325}{
    \raisebox{-0.05\height}{\faPhone}\ +91 8421451325} ~ | ~
  \href{mailto:vaishnavdhanwate2512@gmail.com}{
    \raisebox{-0.15\height}{\faEnvelope}\ vaishnavdhanwate2512@gmail.com} ~ | ~
  \href{https://www.linkedin.com/in/vaishnav-dhanwate}{
    \raisebox{-0.15\height}{\faLinkedin}\ LinkedIn-vaishnav-dhanwate} ~ | ~
  \href{https://github.com/vaishnavSD}{
    \raisebox{-0.15\height}{\faGithub}\ GitHub-vaishnav-dhanwate}
}

%---------%
% Objective %
%---------%
\tinysection{Objective}

Motivated and detail-oriented Web and Mobile App Developer with hands-on experience in building scalable, full-stack, and cross-platform applications using modern technologies. Seeking to contribute creativity and technical expertise in developing web and mobile solutions that enhance user experience and efficiency.

%------------%
% Experience %
%------------%
\vspace{10pt}
\section{Experience}

\headingBf{Netleap IT Training | Web Developer Intern}{Jan 2025 -- Feb 2025}
\headingIt{Nashik, Maharashtra}{}
\begin{resume_list}
  \item Designed and implemented \textbf{responsive UI components} for web applications using \textbf{HTML, CSS, and JavaScript}.
  \item Built and maintained backend functionality and REST APIs using \textbf{Node.js} and managed data with \textbf{MySQL}.
  \item Collaborated with the team on debugging, testing, and ensuring cross-browser compatibility.
\end{resume_list}

%-----------%
% Projects %
%-----------%
\vspace{10pt}
\section{Projects}

\headingBf{ScrapWale -- Online Scrap Collection Platform (Sponsored Project)}{Oct 2025 - Ongoing}
\begin{resume_list}
  \item Developed a full-stack, cross-platform (web and mobile-enabled) solution to streamline scrap collection and management.
  \item Designed and implemented separate user and agent dashboards for tracking collection requests, user details, and delivery status.
  \item Built using \textbf{React Native (Expo)} for the frontend, \textbf{Node.js} for the backend, and \textbf{MySQL} for the database.
\end{resume_list}

\headingBf{Online Course Selling Website}{Feb 2025 -- Mar 2025}
\begin{resume_list}
  \item Developed a full-stack web application for selling courses using \textbf{HTML, CSS, JavaScript, and PHP}.
  \item Integrated core functionalities including user \textbf{authentication}, course listings, and a simple \textbf{checkout flow}.
  \item Utilized \textbf{MongoDB} for efficient backend data storage and management.
\end{resume_list}

\headingBf{Hostel Assistance Clone}{Oct 2024 -- Nov 2024}
\begin{resume_list}
  \item Created a smart web-based system to efficiently manage comprehensive hostel records, including student and employee details.
  \item Implemented full \textbf{CRUD} (Create, Read, Update, Delete) operations and a responsive dashboard for data visualization.
\end{resume_list}

%-----------%
% Education %
%-----------%
\vspace{10pt}
\section{Education}

\headingBf{Bachelor of Engineering (Computer Engineering)}{2026}
\headingIt{G.E.S. R.H. Sapat College of Engineering and Management Studies, Nashik}{}

\vspace{5pt}
\headingBf{Higher Secondary Certificate (HSC) - 78.80\%}{2022}
\headingIt{Sanjivani Sainiki School and Jr. College}{}

\vspace{5pt}
\headingBf{Secondary School Certificate (SSC) - 82.80\%}{2020}
\headingIt{S.G.V.Naur}{}


%--------%
% Skills %
%--------%
\vspace{10pt}
\section{Skills}

\begin{itemize}[itemsep=-2px, parsep=1pt, leftmargin=130pt]
  \item[\textbf{Programming Languages:}] Python, Java
  \vspace{5pt}
  \item[\textbf{Web Technologies:}] HTML, CSS, JavaScript, \textbf{React Native (Expo)}
  \vspace{5pt}
  \item[\textbf{Backend \& Databases:}] \textbf{Node.js}, \textbf{MySQL}, MongoDB, PHP
  \vspace{5pt}
  \item[\textbf{Soft Skills:}] Leadership, Problem Solving, Team Collaboration
\end{itemize}

\end{document}